Figures and tables for paper

### 2021-12-08 analysis/03_analysis.Rmd
Cleaned up import/export to match new location for model runs and posterior draws

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 1234
)
run <- list(data = data, fit = fit)
if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions_5e.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
# Load all model output
intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
political_ideology_run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
social_views_run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
charity_voluntarism_run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
demographics_run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
public_political_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
public_political_social_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
public_political_social_charity_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
public_political_social_charity_demo_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

# Load and extract data and model output
if (intercept == 1 & interactions == 0) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions_5d.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1 & interactions == 0) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions_5d.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

>>>>

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 1234
)
run <- list(data = data, fit = fit)
if (intercept == 1 & interactions == 0) write_rds(run, here::here("data", "raw_data", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "interactions_5e.rds"))
if (public_affairs == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
# Load all model output
intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

# Load and extract data and model output
if (intercept == 1 & interactions == 0) run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "interactions_5d.rds"))
if (public_affairs == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1 & interactions == 0) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
if (public_affairs == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"))
```

### 2021-12-08 analysis/04_figs-tables.Rmd
Cleaned up import/export to match new location for model runs and posterior draws

    here::here("analysis", "output", "posterior_draws", "intercept.rds")

@@

    here::here("analysis", "output", "posterior_draws", "interactions.rds")

@@

    here::here("analysis", "output", "posterior_draws", "public_affairs.rds")

@@

    here::here("analysis", "output", "posterior_draws", "political_ideology.rds")

@@

    here::here("analysis", "output", "posterior_draws", "social_views.rds")

@@

    here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds")

@@

    here::here("analysis", "output", "posterior_draws", "demographics.rds")

@@

    here::here("analysis", "output", "posterior_draws", "public_political.rds")

@@

    here::here("analysis", "output", "posterior_draws", "public_political_social.rds")

@@

    here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds")

>>>>

    here::here("data", "raw_data", "posterior_draws", "intercept.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "interactions.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "public_affairs.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "political_ideology.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "social_views.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "charity_voluntarism.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "demographics.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "public_political.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "public_political_social.rds")

@@

    here::here("data", "raw_data", "posterior_draws", "public_political_social_charity.rds")
